|

### 2022-07-27 manuscript.Rmd
add sonify code and example

Our definition of sonification refers to a data representation method using stereo sound and various audible patterns. For example, Figure \ref{fig:plot-xy} can be made audible by using `sonify` package [@R-sonify] via `r sonify::sonify(x = 1:5, y = 1:5)`.
In this example, a scatter plot is represented by a sound. Position on the X axis is communicated using the left-to-right stereo effect; the pitch of the sound indicates position on the Y axis.

@@

<!-- ```{r sonify-x-y, echo=TRUE, include=TRUE}
# Representing the relationship between the two numerical variables via stereo sound
library(sonify())
sonify(x, y)
``` -->

@@

```{r tactile-producing-code, echo=TRUE, include=TRUE}
library(palmerpenguins)
library(tactileR)

@@

```{r tactile-example, fig.cap="Ready-to-print tactile graph in braille.", fig.alt="Boxplot showing the different body mass between penguins species"}
knitr::include_graphics("figure/tactile-boxplot.pdf")
```

>>>>

Our definition of sonification refers to a data representation method using stereo sound and various audible patterns. For example, Figure \ref{fig:plot-xy} can be made audible by using `sonify` package [@R-sonify] like below.

```{r sonify-x-y, echo=TRUE, include=TRUE, cache=TRUE}
# Representing the relationship between the two numerical variables via stereo sound
library(sonify())

# Prepare variables
x <- 1:5
y <- 1:5

sonify(x, y)
```

In this example, a scatter plot is represented by a sound. Position on the X axis is communicated using the left-to-right stereo effect; the pitch of the sound indicates position on the Y axis.

@@

@@

```{r tactile-producing-code, echo=TRUE, include=TRUE, cache=TRUE}
library(palmerpenguins)
library(tactileR)

@@

```{r tactile-example, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, dependson="tactile-producing-code", fig.cap="Ready-to-print tactile graph in braille.", fig.alt="Boxplot showing the different body mass between penguins species"}
knitr::include_graphics("figure/tactile-boxplot.pdf")
```
